A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-05-28 sections/Overview.tex
Some revisions

%-------------------------------------------------------------------------------
\subsection{Judgment Lists}\label{sec:overview:list}
\bruno{Somewhere we should mention the ``Essence of ML type
  inference'' as pointed out by our reviews/comments?}
To avoid the problem of incrementally applying a substitution to remaining
tasks, we can find inspiration in the formulation of constraint solving
algorithms. For instance, the well-known unification
algorithm by \citet{unification} decomposes the problem of unifying two terms $s \stackrel{.}{=} t$ into a number
of related unification problems between pairs of terms $s_i \stackrel{.}{=} t_i$. These smaller
problems are not tackled independently, but kept together in a set $S$. 
The algorithm itself is typically formulated as a small-step-style state
transition system $S \rightarrowtail S'$ that rewrites the set of unification
problems until it is in solved form or until a contradiction has been found.
For instance, the variable elimination rule is written as:
\[
   x \stackrel{.}{=} t, S  ~~\rightarrowtail~~  x \stackrel{.}{=} t, [t/x]S   \qquad\qquad{if}~x \not\in t~\text{and}~{x \in S}
\]
Because the whole set is explicitly available, the variable $x$ can be
simultaneously substituted everywhere.

In the above unification problem, all variables are implicitly bound in the same
global scope. Recent unification algorithms for dependently-typed languages
are more explicit about scopes. For instance, \citet{Reed2009} represents a unification
problem as $\Delta \vdash P$ where $P$ is a set of equations to be solved and $\Delta$ is
a (modal) context. \citet{Abel2011higher} even use multiple contexts within a unification problem.
Such a problem is denoted $\Delta \Vdash \mathcal{K}$ where the meta-context
$\Delta$ contains all the typings of meta-variables in the constraint set
$\mathcal{K}$. The latter consists of constraints like $\Psi \vdash M = N : C$
that are equipped with their individual context $\Psi$. While accurately tracking
the scoping of regular and meta-variables, this approach is not ideal because it
repeatedly copies contexts when decomposing a unification problem, and
later it has to 
substitute solutions into these copies.

>>>>

%-------------------------------------------------------------------------------
\subsection{Judgment Lists}\label{sec:overview:list}
To avoid the problem of incrementally applying a substitution to remaining
tasks, we can find inspiration in the formulation of constraint solving
algorithms. For instance, the well-known unification
algorithm by \citet{unification} decomposes the problem of unifying two terms $s \stackrel{.}{=} t$ into a number
of related unification problems between pairs of terms $s_i \stackrel{.}{=} t_i$. These smaller
problems are not tackled independently, but kept together in a set $S$. 
The algorithm itself is typically formulated as a small-step-style state
transition system $S \rightarrowtail S'$ that rewrites the set of unification
problems until it is in solved form or until a contradiction has been found.
For instance, the variable elimination rule is written as:
\[
   x \stackrel{.}{=} t, S  ~~\rightarrowtail~~  x \stackrel{.}{=} t, [t/x]S   \qquad\qquad{if}~x \not\in t~\text{and}~{x \in S}
\]
Because the whole set is explicitly available, the variable $x$ can be
simultaneously substituted everywhere.

In the above unification problem, all variables are implicitly bound in the same
global scope. 
\bruno{Some constraint solving algorithms for Hindley-Milner type
  inference use similar ideas, but are more careful tracking the
  scopes of variables~\cite{}. However they have separate phases for 
constraint generation and solving.}
Recent unification algorithms for dependently-typed languages
are also more explicit about scopes. For instance, \citet{Reed2009} represents a unification
problem as $\Delta \vdash P$ where $P$ is a set of equations to be solved and $\Delta$ is
a (modal) context. \citet{Abel2011higher} even use multiple contexts within a unification problem.
Such a problem is denoted $\Delta \Vdash \mathcal{K}$ where the meta-context
$\Delta$ contains all the typings of meta-variables in the constraint set
$\mathcal{K}$. The latter consists of constraints like $\Psi \vdash M = N : C$
that are equipped with their individual context $\Psi$. While accurately tracking
the scoping of regular and meta-variables, this approach is not ideal because it
repeatedly copies contexts when decomposing a unification problem, and
later it has to 
substitute solutions into these copies.

### 2019-05-28 sections/Related.tex
Some revisions

>>>>

\paragraph{The Essence of ML Type-Inference} \bruno{we deal with
  higher-ranked polymorphism and do not have separate phases for 
constraint generation and solving. In such multi-phase algorithms 
there is typically a different constraint language. In contrast in our
single phase algorithm one could view the judgements as a form 
of constraints, and no separate constraint language is needed.
Other more technical differences?}
